High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-21 doc/asplos2013/interface.tex
Major edits to the interface section

\subsection{Machine Interface}
\label{subsec:machmodel}
The last component of the interface allows for introspection of the current machine.
Listing~\ref{lst:machineapi} shows the machine interface.
The {\tt Machine} object is a singleton object that serves two purposes.  First, it
is the mechanism for initializing the runtime; at the start of a program the programmer
creates a machine object and invokes the {\tt run} method (line 30-31).
Second, the machine object provides an interface for the programmer to 
discover properties of the underlying machine (lines 35-43).  The machine object maintains
sets of all the unique {\tt Processor} and {\tt Memory} handles in the system.  Processors
were described in Section~\ref{subsec:procs}.  For every memory in the system there also 
exists a {\tt Memory} handle with a unique ID.  Different memories often, but not always, 
imply a different address space.  Examples of different memories are described in
Section~\ref{sec:impl}.

@@

The machine object also maintains two relations between the set of processors
and the set of memories:
\begin{itemize}
\item Processor-Memory: for each processor-memory pair whether
the processor can directly access (read and write) the memory and 
latency and bandwidth properties if access is possible
\item Memory-Memory: for every pair of memories whether a copy can be
performed between the two memories and latency and
bandwidth properties if a copy is possible
\end{itemize}

The programmer can query these two relations by the {\tt get\_*\_affinity} calls
(lines 40-43).

>>>>

\subsection{Machine Interface}
\label{subsec:machmodel}
The last component of the interface allows for introspection of the current machine.
Listing~\ref{lst:machineapi} shows the machine interface.
The {\tt Machine} object is a singleton object that serves two purposes.  First, it
is the mechanism for initializing the runtime; at the start of a program the client 
creates a machine object, instantiates a task table mapping task IDs to function pointers,
and invokes the {\tt run} method (line 30-31).
Second, the machine object provides an interface for the client to 
discover properties of the underlying machine (lines 35-43).  The machine object maintains
sets of all the unique {\tt Processor} and {\tt Memory} handles in the system.  Processors
were described in Section~\ref{subsec:procs}.  For every memory in the system there also 
exists a {\tt Memory} handle with a unique ID.  Different memories often, but not always, 
imply a different address space.  Examples of different memories are described in
Section~\ref{sec:impl}.

@@

The machine object also maintains two relations between the set of processors
and the set of memories:
\begin{itemize}
\item Processor-Memory: for each processor-memory pair whether
the processor can directly access (read and write) the memory and 
latency and bandwidth properties if access is possible
\item Memory-Memory: for every pair of memories whether copies can be
performed and latency and bandwidth properties if copies are possible
\end{itemize}

The client can query these two relations by the {\tt get\_*\_affinity} calls
(lines 40-43).
